Youtube Trend Exploration by Soumya Ghosh
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(knitr)
library(dplyr)
library(GGally)
library(lubridate)
library(gridExtra)
library(psych)
library(memisc)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
YtUsa <- read.csv("USvideos_modified.csv")

```

This report explores a dataset containing video id,views count,number of 
likes,subscriber and other attributes for approximately 4,600 Youtube 
Trending videos.


# Univariate Plots Section


```{r echo=FALSE, Univariate_Plots}
dim(YtUsa)

```

```{r echo=FALSE}
#converting class of 2 columns
YtUsa$publish_hour <- factor(YtUsa$publish_hour)
YtUsa$category_id <- factor(YtUsa$category_id)
str(YtUsa)
```

```{r echo=FALSE}
summary(YtUsa)
```

Our dataset consists of 23 variables, with 4547 observations.

[Notice - I would create a new variable at Bivariate Plots Section.]

```{r echo=FALSE}
as.Date(YtUsa$last_trending_date[dim(YtUsa)[1]]) - 
  as.Date(YtUsa$last_trending_date[1])
```

So there are total 105 days of observation for Youtube trending videos.

```{r echo=FALSE}
ggplot(aes(x=publish_hour),data=YtUsa)+geom_bar()
```

I can see peak hour for publishing a trending video in Youtube in between 
14:00 to 18:00 in USA timezone.
Though it might be the case, that all videos are published during this hour,
not only trending ones.

```{r echo=FALSE}
ggplot(aes(x=category_id),data=YtUsa)+geom_bar()
```

Youtube category wise distribution.

```{r echo=FALSE}
table(YtUsa$category_id)
```

It can be clearly seen ,category_id = 24 is the category where highest 
number(1102) of Youtube trending videos were published.

```{r echo=FALSE}
ggplot(aes(subscriber),data=YtUsa[!is.na(YtUsa$subscriber),])+
  geom_histogram(binwidth=1000000)+scale_x_continuous(
    breaks=seq(0,1000000000,5000000))+
  ggtitle("Distribution of Subscribers")+labs(caption="bin width = 1000000")
```

```{r echo=FALSE}
summary(YtUsa$subscriber)
```

There are 22 trending video where subscriber information set to NA.

```{r echo=FALSE}
ggplot(aes(tags_count),data=YtUsa)+geom_histogram(binwidth=1)
```

```{r echo=FALSE}
table(YtUsa$tags_count)
```

We can see , there are 208 videos which are not using any tag.

```{r}
#by which.max() trying to find the index of maximum value of the table 
# generated from 'tags_count' column.And then using that index,find out the 
# table content.So generally that will be the mode of the column & frequency.

table(YtUsa$tags_count)[which.max(table(YtUsa$tags_count))]
```


mode of tags_count is 0.

```{r echo=FALSE}
median(YtUsa$tags_count)
```


Median tags_count is 18.

```{r echo=FALSE}
ggplot(aes(x=tag_appeared_in_title_count),data=YtUsa)+
  geom_histogram(binwidth = 1)+scale_x_continuous(breaks = seq(0,18,1))
```

```{r echo=FALSE}
summary(YtUsa$tag_appeared_in_title_count)
```

From the Histogram & the summary ,we can see, Q3-Q1=68% of the Youtube 
trending videos are using 1 to 4 tags those are also appeared in the 
video title.

```{r echo=FALSE}
summary(YtUsa$tag_appeared_in_title)
```

Out of 4547 trending videos , 701 video title had not used any of its tag
(or keyword) on the video title.

```{r echo=FALSE}
ggplot(aes(x=trend_day_count),data=YtUsa)+geom_histogram(binwidth = 1)
```
```{r echo=FALSE}
summary(YtUsa$trend_day_count)
```


```{r echo=FALSE}
table(YtUsa$trend_day_count)
```

From 105 days of observation , it can be seen ,that a particular video 
trended for 14 days at most.

We can see there are 604 videos those had appeared in the Youtube trending 
video list for only once.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x=comment_count),data=YtUsa)+
  geom_histogram()+scale_x_continuous(lim = c(0,10000))+
  ggtitle("comment_count distribution upto 10000")
```

```{r echo=FALSE, message=FALSE}
ggplot(aes(x=comment_count+1),data=YtUsa)+geom_histogram()+scale_x_log10()+
  labs(caption = "scale_x_log10()")
```

Long tailed distribution transformed for better understanding of the comment
counts.
Since we are using log10 transformation on x-axis for comment_count, we have
to apply comment_count+1 to overcome Infinite values.


```{r echo=FALSE}
summary(YtUsa$comments_disabled)
```

There are only 76 videos where comments_disabled variable set to True.

```{r echo=FALSE,message=FALSE}
ggplot(aes(x=trend.publish.diff+1),data=YtUsa)+geom_histogram()+
  scale_x_log10(breaks=c(1:7,14,90,30,365,1000,4215))+
  ggtitle("Distribution of difference between video publishing date & video 
          trending date(1st time)")+
  labs(caption = "scale_x_log10() ; video trending date(1st time) - video 
       publish date")
```

We can see,maximum number of Youtube videos are listed on trending, within 0
to 14 days of the video publishing date.

```{r echo=FALSE}
ggplot(aes(x=as.Date(last_trending_date)),data=YtUsa)+geom_bar()+
  scale_x_date()+labs(caption = "scale_x_date()")
```

2 days trending data are missing in mid January.

```{r echo=FALSE, message=FALSE}
plt1 <- ggplot(aes(x=trend_tag_highest),data=subset(YtUsa,!is.na(tags)))+
  geom_histogram()
plt2 <- ggplot(aes(x=trend_tag_total),data=subset(YtUsa,!is.na(tags)))+
  geom_histogram()
grid.arrange(plt1,plt2)
```

We can clearly see ,there is multi-modal distribution over trend_tag_highest.
And trend_tag_total distribution is long tailed positively(right) skewed.
Both of them are under non-symmetric distribution.

```{r echo=FALSE, message=FALSE}
plt3 <- ggplot(aes(x=trend_tag_highest),data=subset(YtUsa,!is.na(tags)))+
  geom_histogram()+scale_x_log10()+labs(caption = "scale_x_log10()")
plt4 <- ggplot(aes(x=trend_tag_total),data=subset(YtUsa,!is.na(tags)))+
  geom_histogram()+scale_x_log10()+labs(caption = "scale_x_log10()")
grid.arrange(plt3,plt4)
```

log10() applied on both of the x scale.


Now I am plotting distribution of some key features of the dataset with 
log10 transformation.

```{r fig.width=9, fig.height=15 ,echo=FALSE, message=FALSE}
plot1 <- ggplot(aes(views),data=YtUsa)+geom_histogram()+scale_x_log10()+
  ggtitle("Distribution of views scaled to log10")
plot2 <- ggplot(aes(likes+1),data=YtUsa)+geom_histogram()+scale_x_log10()+
  ggtitle("Distribution of likes scaled to log10")
plot3 <- ggplot(aes(dislikes+1),data=YtUsa)+geom_histogram()+scale_x_log10()+
  ggtitle("Distribution of dislikes scaled to log10")
plot4 <- ggplot(aes(subscriber+1),data=subset(YtUsa,!is.na(subscriber)))+
  geom_histogram()+scale_x_log10()+
  ggtitle("Distribution of subscribers scaled to log10")
grid.arrange(plot1,plot2,plot3,plot4,ncol=1)
```



# Univariate Analysis


### What is the structure of your dataset?

There are 4,547 unique video ids(observations) in the dataset with 23 
features.15 of them are independent feature & rest of them are dependent
feature."video_id" is the unique feature of the dataset.

Trending report recorded for 105 days.
Category id 24 is the most used category for trending videos.
1,102 of 4,547 videos were published under that category.
From 105 days of observation ,we observed that no video repeated(re-trended) 
on trending list for more than 14 times.
It is also observed that most of the videos get listed on Youtube trending 
list within 0 to 14 days of video publishing date.
84% or more trending videos are using one of its tag on the video title for 
at least once. 

The Median views for a Youtube trending video = 318840.
The Median comment count for a Youtube trending video = 854.
Maximum number of dislikes a Youtube trending video got 1674420.
The Median subscriber count for a Youtube trending video = 1198769.
208 trading videos did not include any tag on the video.
604 videos were trended for only once, means those video were never 
re-trended within 105 days of period.


### What is/are the main feature(s) of interest in your dataset?

Main features in the dataset are: views,comment_count,likes,dislikes & 
subscriber.
I like to determine which features are best for predicting the views of a 
Youtube trending video.
I suspect comment_count,likes,dislikes,subscriber and some combination of the
other features could be used to build a predictive model to determine views 
count of a Youtube trending video.


### What other features in the dataset do you think will help support your 
#     investigation into your feature(s) of interest?

Other features in the dataset are : 
category_id,
tag_appeared_in_title,
trend_tag_highest(Maximum number of times all trending videos used one of the 
tag,which is used on the video),
trend_tag_total(Total number of times all trending videos used any of the tag
,which are used for the video),
trend_day_count(Number of times a video listed on Youtube Trend).


### Did you create any new variables from existing variables in the dataset?

Yes ,I created 5 new variables those could be derived from the dataset,
names are :
tag_appeared_in_title_count,tag_appeared_in_title,trend_tag_highest,
trend_tag_total,tags_count.


### Of the features you investigated, were there any unusual distributions?
#     Did you perform any operations on the data to tidy, adjust,or change 
#     the form of the data? If so, why did you do this?

When I investigate ,I found only 76 observations, where comments_disabled 
feature is enabled.
Also found only 25 observations with ratings_disabled feature enabled.
These numbers are very low in respect of total number of observations.
I think ,those two are important features of the dataset ,but due to lack of
their availability,we would not be confident to make any assumption based 
upon them.

Yes I performed operations on the original dataset to make it tidy.So this 
dateset is modified version of the original one.
In original dataset there were multiple observation for same video_id .
That original dataset could be used for observation as a time series,
but as you could see from the feature "trend_day_count" ,not all video_id(s) 
were repeated in Youtube trending. Therefore time series not available for 
every video.
So for that case, I had to filter trend_day_count > 1 & that would remove 604 
trending videos.
But for this project ,I liked to observe each & every trending videos.



# Bivariate Plots Section

```{r echo=FALSE ,fig.width= 15,fig.height=9, Bivariate_Plots}

pairs(YtUsa[,c(4:5,7:12,14,18:23)],bg=c("yellow","blue"), pch = 21)

```

```{r echo=FALSE,fig.width= 15,fig.height=9}

pairs.panels(YtUsa[,c(4:5,7:12,14,18:23)],method = "pearson",hist.col = 
               "#00AFBB",density = TRUE,ellipses = TRUE)

```

One of the interesting point I would like to share,correlation between likes 
& comment_count = 0.71 .
And correlation between dislikes & comment_count = 0.83 .
So we can claim, that more people involved in conversation when they were 
disliking a video rather than liking a video.
Most of these cases ,video might be controversial or a fake news,etc.

```{r echo=FALSE, message=FALSE}
ggplot(aes(y=views,x=likes+1),data=YtUsa)+geom_jitter(alpha=0.25,size=3/4)+
  scale_x_log10(breaks=c(1,100,1000,10000,100000,1000000))+scale_y_log10()+
  xlab("likes")+labs(caption="scale_x_log10()+scale_y_log10()")+
  ggtitle("Views v/s Likes+1 with log10 transformation for both axes")+
  geom_smooth()
```

```{r echo=FALSE}
with(YtUsa,cor(views,likes))
```
 
From the above plot we can see, there is a very strong relationship between 
views & likes.
And the value of the correlation between them is 0.82.

Since log10 applied on the x-axis & and there are few videos in Youtube 
trending list with 0 likes, thats why we have to pass the variable (likes+1) 
instead of likes into the scale_x_log10() function. That would help to 
overcome infinite values(since log10(0) = Inf).

Therefore in the above plot on x-axis scale 1 represent 0.

We can see there are many outliers on y-axis for x = 1.
Many of those video authors might be disabled video rating ,so users can't 
like or dislike the video.

Another point to see,after 10^4=10000 likes ,variance of likes decreases as 
views increases.

```{r echo=FALSE}
ggplot(aes(y=views,x=dislikes+1),data=YtUsa)+
  geom_jitter(alpha=0.25,size=3/4)+scale_x_log10(
    breaks=c(1,100,1000,10000,100000))+scale_y_log10()+
  labs(caption="scale_x_log10()+scale_y_log10()")+
  ggtitle("Views v/s Dislikes+1 with log10 transformation for both axes")
```

Plot almost looks similar to views v/s likes plot, but in this case ,variance
of dislikes is bigger for some places.

```{r echo=FALSE}
with(YtUsa,cor(views,dislikes))
```

Correlation between views & dislikes =  0.53 .

```{r echo=FALSE}
# Finding correaltion between views & (likes/dislikes)
# In the dataset, there are few data points with likes=0 & dislikes=0
#  and that would cause Inf, so we need to subset the dataset, by extracting 
#  those data points.
with(subset(YtUsa,likes !=0 & dislikes != 0),cor(views,likes/dislikes))
```

Correlation between views and ratio of the likes & dislikes is very weak.

```{r echo=FALSE}
with(subset(YtUsa,likes !=0 & comment_count != 0),cor(likes,comment_count))
```

Correlation between views and comment_count is vey strong.

```{r echo=FALSE, message=FALSE}
ggplot(aes(y=views,x=nchar(as.character(description))),data=YtUsa)+
  geom_point(alpha=0.1,position = "jitter")+
  coord_cartesian(xlim=c(quantile(
    nchar(as.character(YtUsa$description)),0.0),quantile(
      nchar(as.character(YtUsa$description)),0.95)),
    ylim=c(quantile(YtUsa$views,0.0),quantile(YtUsa$views,0.95)))+
  geom_smooth()+scale_y_log10(breaks=c(1,100000,300000,1000000))+
  labs(caption = "scale_y_log10()")+
  ggtitle("views v/s description length relation")+
  xlab("description length")
```

Trending videos with less than 500 video description length has lower 
mean(average) views count than others. 
[Please see - we observed top 95% CI]

```{r echo=FALSE, message=FALSE}
ggplot(aes(y=views,x=nchar(as.character(title))),data=YtUsa)+
  geom_point(alpha=0.05)+scale_y_log10(breaks=c(
    1,100000,200000,300000,1000000))+geom_smooth()+
  labs(caption = "scale_y_log10()")+
  ggtitle("views v/s title length relation")+xlab("title length")
```

From the above plot,linear regression line represents,as the average length 
of video titles are increasing, average views counts are slightly decreasing.

```{r echo=FALSE, message=FALSE}
ggplot(aes(y=views,x=tag_appeared_in_title_count),data=YtUsa)+
  geom_point(alpha=0.1,position = "jitter")+coord_cartesian(xlim=c(quantile(
    YtUsa$tag_appeared_in_title_count,0.025),quantile(
      YtUsa$tag_appeared_in_title_count,0.975)),ylim=c(quantile(
        YtUsa$views,0.025),quantile(YtUsa$views,0.975)))+geom_smooth()+
  scale_y_log10(breaks=c(0,100000,200000,500000,1000000,10000000))+
  labs(caption = "scale_y_log10()")
```

tag_appeared_in_title_count not much effecting count of views.
[Please see - we observed 2-tailed 95% CI]

```{r echo=FALSE}
with(YtUsa,cor(views,tag_appeared_in_title_count))
```

As like expected correlation between views & tag_appeared_in_title_count = 
0.02,which is very weak.

```{r echo=FALSE, message=FALSE}
ggplot(aes(y=views,x=trend_day_count),data=YtUsa)+
  geom_point(position ="jitter",alpha=.1)+coord_cartesian(xlim=c(0,quantile(
    YtUsa$trend_day_count,0.95)),ylim=c(0,quantile(YtUsa$views,0.95)))+
  geom_smooth()
```

```{r echo=FALSE}
with(YtUsa,cor(views,trend_day_count))
```

For top 95% of the views counts & trend_day_count data, we can say ,as mean 
trend_day_count are increasing mean views counts are increasing rapidly.

Correlation between views & trend_day_count = 0.19 

```{r echo=FALSE}
with(YtUsa,cor(views,trend_day_count,method = "spearman"))
```

Rank correlation(method="spearman") between views & trend_day_count is 
0.3594205


```{r echo=FALSE, message=FALSE}
ggplot(aes(y=views,x=as.numeric(category_id)),data=YtUsa)+
  geom_jitter(alpha=0.25,color="orange")+coord_cartesian(ylim=c(0,quantile(
    YtUsa$views,0.95)))+geom_smooth()+
labs(caption="smoothing attempted after converting category_id from factor 
to numeric") 
```

Video category_id related with views counts.

```{r echo=FALSE}
with(YtUsa,cor(views,as.numeric(category_id),method = "pearson"))
```

And the value of correlation is -0.116636 (-0.12)

```{r}
# Finding correlation between views & category_id only for top 95% CI of 
#   views
# Since class of category_id is factor, we need to change it to numeric for
#   correlation calculation.

with(subset(YtUsa,views >= quantile(views,0.0) & views <= 
              quantile(views,0.95)),cor(views,as.numeric(category_id)))
```

Correlation between top 95% of views & category_id = -0.1038592


To make more sense about categorical distribution,lets create a new variable 
called "subscriber_by_category",which will represent 3 groups of data.

low : group of all categort_id's those have small(<=7552015) number of 
subscribers.
medium : group of all categort_id's those have moderate(from 7552016 to 
18185017) number of subscribers.
high : group of all categort_id's those have huge(>18185017) number of 
subscribers.

Here, low < medium < high

```{r}
# remember subscriber have NA's, so we need to use a subset of the dataset.
# group by category_id

cat_groups <- group_by(subset(YtUsa,!is.na(subscriber)),category_id)
YtUsa.subs_by_cat <- summarise(cat_groups,subs_max = max(subscriber),n=n())
YtUsa.subs_by_cat <- arrange(YtUsa.subs_by_cat,subs_max)

#Here YtUsa.subs_by_cat is a new data.frame containing 3 columns:
# category_id,subs_max,n

#subs_max would represent the highest subscriber of a video channel for that
# Youtube category_id
#n represent number of Youtube trending videos are present in the category.
```


```{r}
YtUsa$subscriber_by_category <- NA # new variable created & NA assigned to 
# its all values.

#now assigning new values from YtUsa.subs_by_cat DataFrame as per conditions

YtUsa[YtUsa$category_id %in% 
        YtUsa.subs_by_cat[YtUsa.subs_by_cat$subs_max<=7552015,]
      $category_id,]$subscriber_by_category <- "low"

YtUsa[YtUsa$category_id %in% 
        YtUsa.subs_by_cat[YtUsa.subs_by_cat$subs_max> 7552015 & 
                            YtUsa.subs_by_cat$subs_max<=18185017,]
      $category_id,]$subscriber_by_category <- "medium"

YtUsa[YtUsa$category_id %in% 
        YtUsa.subs_by_cat[YtUsa.subs_by_cat$subs_max>18185017,]
      $category_id,]$subscriber_by_category <- "high"

# change variable class to factor
YtUsa$subscriber_by_category <- factor(YtUsa$subscriber_by_category)

# ordered to low < medium < high
YtUsa$subscriber_by_category <- 
  ordered(YtUsa$subscriber_by_category,levels=c(
    levels(YtUsa$subscriber_by_category)[2:3],
    levels(YtUsa$subscriber_by_category)[1]))
```


```{r}
#To calculate cor, variables must be numeric, that's why, converting  
# subscriber_by_category low,medium,high to numeric 1,2,3.

with(YtUsa,cor(views,as.numeric(subscriber_by_category)))
```

correlation in between views & subscriber_by_category = 0.10

```{r echo=FALSE}
ggplot(aes(y=views,x=subscriber_by_category),data=YtUsa)+
  geom_point(position ="jitter",alpha=0.1)+scale_y_sqrt()+
  labs(caption="scale_y_sqrt()")
```

So categories with greater level of subscribers have more chance of getting 
more Youtube viewers.

```{r echo=FALSE}
by(YtUsa$views,YtUsa$subscriber_by_category,summary)
```

```{r echo=FALSE}
ggplot(aes(y=views,x=subscriber_by_category),data=YtUsa)+
  geom_boxplot()+scale_y_log10(breaks=c(
    10000,33768,144773,287705,406864,1315056))+
  labs(caption="scale_y_log10()")
```

It can be seen that  1st Quantile, Median & 3rd Quantile views counts are 
highly affected by the 'subscriber_by_category' feature.

```{r echo=FALSE}
ggplot(aes(x=likes,y=dislikes),data=subset(YtUsa,likes!=0 & dislikes!=0))+
  geom_point(alpha=0.1)+scale_x_log10()+scale_y_log10()+
  geom_smooth(method="lm")+labs(caption="scale_x_log10()+scale_y_log10()")
```

```{r echo=FALSE}
with(YtUsa,cor(likes,dislikes,method = "pearson"))
```

Likes & Dislike has a strong relationship with correlation value of 0.46

```{r echo=FALSE, message=FALSE}
ggplot(aes(y=views,x=comment_count+1),data=YtUsa)+geom_point(alpha=.1)+
  scale_x_log10(breaks=c(1,10,100,100000,1000000))+
  scale_y_log10(breaks=c(500,1000,10000,100000,1000000,10000000,100000000))+
  geom_smooth()+labs(caption = "scale_x_log10() & scale_y_log10()")
```

```{r echo=FALSE}
with(YtUsa,cor.test(views,comment_count))
```

Correlation(method=pearson) between views & comment_count is very strong & 
its value is 0.5733848

```{r echo=FALSE ,warning=FALSE}
with(YtUsa,cor.test(views,comment_count,method = "spearman"))
```

rho is a nonparametric measure of rank correlation.
rho between views & comment_count is very strong too.And its value is 
0.8252309 

```{r echo=FALSE, message=FALSE}
ggplot(aes(y=views,x=trend_tag_highest),data=YtUsa)+geom_point(alpha=.1)+
  scale_y_log10()+geom_smooth()+labs(caption = "scale_y_log10()")
```

Regression Line for views v/s trend_tag_highest is monotonic here.

```{r echo=FALSE}
with(YtUsa,cor(views,trend_tag_highest))
```

And correlation between views & trend_tag_highest is -0.013 here.

```{r echo=FALSE, message=FALSE}
ggplot(aes(y=views,x=trend_tag_total),data=YtUsa)+geom_point(alpha=.1)+
  scale_y_log10()+geom_smooth()+labs(caption = "scale_y_log10()")
```

```{r echo=FALSE}
with(YtUsa,cor(views,trend_tag_total))
```

Relationship between views & trend_tag_total is non linear.

```{r echo=FALSE}
ggplot(aes(y=views,x=factor(trend_day_count)),data=YtUsa)+geom_boxplot()+
  scale_y_log10()+
  labs(caption = "scale_y_log10() applied.And trend_day_count converted to 
       factor for categorizing")
```

Now Boxplots for views v/s trend_day_count for 2 tailed 95% CI :-

```{r echo=FALSE}
ggplot(aes(y=views,x=factor(trend_day_count)),data=YtUsa)+geom_boxplot()+
  coord_cartesian(ylim=c(quantile(YtUsa$views,.025),quantile(
    YtUsa$views,.975)))+scale_y_log10()+labs(caption = "scale_y_log10()")
```

```{r echo=FALSE}
by(YtUsa$views,YtUsa$trend_day_count,summary)
```

Median views count for trend_day_count : 1  = 163307 .
Median views count for trend_day_count : 14  = 17540613 .
And 17540613 >> 163307 .
So if a video get listed more times on Youtube trending,its median views 
count is way more bigger(for maximum cases).


```{r echo=FALSE}
ggplot(aes(y=likes+1,x=subscriber_by_category),data=YtUsa)+
  geom_boxplot()+scale_y_log10(breaks=c(
    500,1011,8843,20000,33120))+
  labs(caption="scale_y_log10()")
```

```{r echo=FALSE}
with(YtUsa,by(likes,subscriber_by_category,summary))
```

Median likes count for low group of 'subscriber_by_category' is far lower 
than the median likes count for medium & high.  

```{r echo=FALSE}
ggplot(aes(subscriber_by_category,subscriber),
       data=YtUsa[!is.na(YtUsa$subscriber),])+
  geom_jitter(alpha=0.25,color="green",size=2)+
  labs(caption="x -> median\n + -> mean")+
  ggtitle("Subscriber v/s subscriber_by_category")+
  stat_summary(fun.y=median,geom="point",shape=4)+
  stat_summary(fun.y=mean,geom="point",shape=3)
```


```{r echo=FALSE}
with(YtUsa,by(subscriber,subscriber_by_category,summary))
```

Median subscriber for subscriber_by_category: low = 599310 .
Median subscriber for subscriber_by_category: medium = 1099202 .
Median subscriber for subscriber_by_category: high = 1759496 .

```{r echo=FALSE}
ggplot(aes(y=views,x=tag_appeared_in_title),data=YtUsa)+geom_boxplot()+
  scale_y_log10()+labs(caption = "scale_y_log10()")
```

Boxplots for views v/s tag_appeared_in_title for 2 tailed 95% CI shown below:

```{r echo=FALSE}
ggplot(aes(y=views,x=tag_appeared_in_title),data=YtUsa)+geom_boxplot()+
  coord_cartesian(ylim=c(quantile(YtUsa$views,.025),quantile(
    YtUsa$views,.975)))+
  scale_y_log10(breaks=c(53227,100000,247049,333984,1042283))+
  labs(caption = "scale_y_log10()")
```

```{r echo=FALSE}
by(YtUsa$views,YtUsa$tag_appeared_in_title,summary)
```

Median views Value for not tag_appeared_in_title = 247049 .
Median views Value for tag_appeared_in_title = 333984

```{r echo=FALSE, message=FALSE}
ggplot(aes(x=views),data=YtUsa)+geom_histogram()+scale_x_log10()+
  facet_wrap(~tag_appeared_in_title)+
ggtitle("distribution of views in respect of tag_appeared_in_title or not")+
  labs(caption = "scale_x_log10()")
```

From above observations ,we can say,there is a impact on Youtube trending 
videos views count over tag_appeared_in_title or not.

```{r echo=FALSE}
ggplot(aes(x=tag_appeared_in_title_count,fill=tag_appeared_in_title),
       data=YtUsa)+
  geom_histogram(binwidth = 1)+scale_x_continuous(breaks = seq(0,18,1))
```

Above plot showing an obvious point.
If tag_appeared_in_title set to False, then tag_appeared_in_title_count 
should be 0(since one variable derived from another).

```{r echo=FALSE, message=FALSE,warning=FALSE, fig.width= 12,fig.height=8}
plota <- ggplot(aes(x=trend.publish.diff+1,fill=factor(trend_day_count)),
                data=YtUsa)+geom_histogram()+
  scale_x_log10(breaks=c(1:7,14,90,30,365,1000,4215))+
  labs(caption = "scale_x_log10()")+
  ggtitle("Distribution of (trend.publish.diff+1) in log10 scale")

plotb <- ggplot(aes(x=trend.publish.diff,fill=factor(trend_day_count)),
                data=YtUsa)+geom_histogram(binwidth = 1)+
  scale_x_continuous(limits =  c(0,30),breaks=seq(0,30,2))+
  labs(caption = "binwidth=1")+
  ggtitle("Distribution of trend.publish.diff")

grid.arrange(plota,plotb,ncol=1)
```

For a trending Youtube video ,if difference between first trending date & 
publish date is less than 4 days,then it would not be re-trended for more 
than 3 times on Youtube.

```{r echo=FALSE, message=FALSE}
ggplot(aes(x=views),data=YtUsa)+geom_histogram()+scale_x_log10()+
  facet_wrap(~comments_disabled)+
  ggtitle("distribution of views in respect of comments_disabled or not")+
  labs(caption = "scale_x_log10()")
```

```{r echo=FALSE}
by(YtUsa$views,YtUsa$comments_disabled,summary)
```

Though, there are only 76 observations present ,out of 4547 for 
comments_disabled = True.
But still we can see there is a huge impact on Youtube trending videos views 
count over comments_disabled or not.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x=likes/dislikes),data=subset(YtUsa,dislikes !=0))+
  geom_histogram()+scale_x_continuous(limit=c(0,550),breaks=seq(0,550,50)) 
```

Looks like ratio of likes/dislikes is not uniformal for Youtube trending 
videos.
	
```{r echo=FALSE}
ggplot(aes(x=trend_tag_highest),data=subset(YtUsa,!is.na(tags)))+
  geom_histogram(aes(fill=category_id),color="black",binwidth = 25)+
  ggtitle("trend_tag_highest by category_id")
```

It is looks like, most frequently used tags on videos are attached from
caterogoty_id 23 & 24

```{r echo=FALSE ,fig.width=9,fig.height=6}
ggplot(aes(x=trend_day_count,fill=subscriber_by_category),data=YtUsa)+
  geom_histogram(binwidth = 1)+
ggtitle("trend_day_count distribution with respect to subscriber_by_category")
```

Significant amount of videos are re-trended everyday from 
subscriber_by_category: high & subscriber_by_category: medium group.

```{r echo=FALSE}
ggplot(aes(x=trend_day_count),data=YtUsa)+geom_histogram(binwidth = 1)+
  facet_wrap(~tag_appeared_in_title)+
ggtitle("trend_day_count distribution in respect of tag_appeared_in_title 
or not")
```
```{r echo=FALSE}
by(YtUsa$trend_day_count,YtUsa$tag_appeared_in_title,summary)
```

Looks like, number of days a video trended does not much affected by whether
the tag appeared on the video title or not.

```{r echo=FALSE, message=FALSE}
ggplot(aes(y=views,x=tags_count),data=subset(YtUsa,!is.na(tags)))+
  geom_point()+geom_smooth()+scale_y_sqrt()+labs(caption="scale_y_sqrt()")+
  ggtitle("views v/s tags_count")
```

```{r echo=FALSE}
with(subset(YtUsa,!is.na(tags)),cor(views,tags_count))
```

By just observing number of tags(tags_count) attached on a trending video,
we could not say how many views that video would get.

```{r echo=FALSE, message=FALSE}
with(subset(YtUsa,!is.na(subscriber)),ggplot(aes(y=views,x=subscriber),
  data=subset(YtUsa,!is.na(subscriber)))+geom_point()+geom_smooth()+
  ggtitle("Views v/sSubscriber"))+
  scale_x_continuous(breaks=seq(0,1000000000,5000000))
```

There are a good amount of outliers exist in the dataset. This outliers have 
only few number of subscribers and yet they managed to get higher number of 
views count.

```{r echo=FALSE, message=FALSE}
with(subset(YtUsa,!is.na(subscriber)),ggplot(aes(y=views,x=subscriber),
  data=subset(YtUsa,!is.na(subscriber)))+geom_point()+
    coord_cartesian(xlim=c(quantile(subscriber,.025),
                           quantile(subscriber,.975)),
                    ylim=c(quantile(views,.025),quantile(views,.975)))+
    geom_smooth(method="lm",color="red")+
    geom_smooth()+
  ggtitle("Views v/s Subscriber for 2-tailed 95% CI of both variables"))
```

By Applying geom_smooth() with & without linear method(lm), its look like 
average count of views increasing as per average number of subscriber 
increasing.
Though relation is not strong.
[please see - we observerd the data for 2-tailed 95% CI]

```{r echo=FALSE}
with(subset(YtUsa,!is.na(subscriber)),cor(views,subscriber))
```

As like expected ,Correlation coefficient between views & subscriber is 0.27 .


Now I am buiding a linear model for views v/s likes :

```{r echo=FALSE}
#Creating a model to predict views. This model will use 'likes' ,'dislikes',
# 'comment_count', 'subscriber', 'trend_day_count', 'category_id' & other
# variables those are derived from 'tag' variable. We know 'subscriber' & 
# 'tags' variables have NA's. So at first we need to create a subset of the
# dataset

m1 <- lm(I(views) ~ I(likes), data = subset(YtUsa,!is.na(subscriber) & 
                                              !is.na(tags)))
m2 <- update(m1, ~ . + comment_count)
m3 <- update(m2, ~ . + dislikes)
m4 <- update(m3, ~ . + trend_day_count)
m5 <- update(m4, ~ . + category_id)
m6 <- update(m5, ~ . + tag_appeared_in_title)
m7 <- update(m6, ~ . + subscriber)
#mtable(m1, m2, m3, m4, m5,m6,m7,sdigits = 3)
```


```{r echo=FALSE}
summary(m1)
```

For the linear model ,Multiple R-squared value between views & likes = 0.6816


# Bivariate Analysis


### Talk about some of the relationships you observed in this part of the
# investigation.How did the feature(s) of interest vary with other features 
# in the dataset?

Youtube trending videos views counts strongly correlated with likes ,dislikes
,comment_count.
As the likes or dislikes or comment_count increases,views of a video also 
increases. 
The relationship between views count and likes or dislikes or comment_count 
is almost linear.

Linear Coefficient Correlation(method = pearson) between views & likes = 0.82

Linear Coefficient Correlation(method = pearson) between views & dislikes = 
0.53

Linear Coefficient Correlation(method = pearson) between views & 
comment_count = 0.57

And rank Correlation(method = Spearman) between views & comment_count = 
0.8252309

Point to see, all above correlations are positive & strong.

Linear Correlation coefficient(method = pearson) between views & subscriber
= 0.27

For tag_appeared_in_title: TRUE , median views count is 333984.
For tag_appeared_in_title: FALSE , median views count is 247049.

Median subscriber for subscriber_by_category: low = 599310 .
Median subscriber for subscriber_by_category: medium = 1099202 .
Median subscriber for subscriber_by_category: high = 1759496 .

Most frequestly used tags on videos are attached from caterogoty_id 23 & 24.

Based on the R^2 value,likes explains about 68 percent of the variance in 
views.Other features of interest can be incorporated into the model to 
explain the variance in the views.


### Did you observe any interesting relationships between the other features
# (not the main feature(s) of interest)?

Yes,
Pearson Coefficient Correlation(PCC) value between views & category_id 
is -0.12,
PCC between views & tag_appeared_in_title = 0.01,
PCC between views & trend_tag_highest = -0.01,
PCC between views & trend_tag_total = -0.02,
PCC between views & trend_day_count = 0.19,
PCC in between views & subscriber_by_category = 0.10 .

1st Quantile, Median & 3rd Quantile views counts are highly affected by 
the 'subscriber_by_category' feature.

The relationship between views count and category_id or trend_tag_highest or 
trend_day_count is monotonic.
The relationship between views count and trend_tag_total is non linear.


### What was the strongest relationship you found?

Strongest relation between two feature in the dataset are views & likes.
Coefficient Correlation between them : 0.82


# Multivariate Plots Section


```{r echo=FALSE, Multivariate_Plots}
with(subset(YtUsa,!is.na(subscriber)),ggplot(aes(
  y=views/trend_day_count,x=subscriber),data=subset(
    YtUsa,!is.na(subscriber)))+
  geom_point(alpha=0.2,position = "jitter",size=3)+
  scale_y_sqrt(breaks=c(100000,1000000,10000000))+
  scale_x_continuous(breaks=c(0,5000000,10000000,20000000,25000000))+
  facet_wrap(~subscriber_by_category,ncol=1)+
ggtitle("Views/day v/s Subscriber categorized by subscriber_by_category"))+
  labs(caption="scale_y_sqrt()")
```


Trend showing ,variance of views per day is getting bigger for higher number
of subscriber groups.

```{r echo=FALSE}
ggplot(aes(y=views,x=trend_day_count,color=tag_appeared_in_title),
       data=YtUsa)+geom_point(position = "jitter",alpha=1)+
  coord_cartesian(ylim=c(0,quantile(YtUsa$views,0.95)))+
  ggtitle("top 95% views v/s trend_day_count by tag_appeared_in_title")
```

By just seeing how many times a video get appeared on the Youtube trend,we 
can't imagine how many views a video can get,because variance of views for 
each day is very big.So range is very bigger here.

```{r echo=FALSE}
ggplot(aes(y=views/trend_day_count,x=subscriber_by_category),data=YtUsa)+
  geom_boxplot()+scale_y_log10(breaks=c(
    1000,10000,36099,62628 ,107318,300000,1000000))+
  labs(caption="scale_y_log10()")+
  ggtitle("views per day v/s subscription wise categories")
```

```{r echo=FALSE}
with(YtUsa,by(views/trend_day_count,subscriber_by_category,summary))
```

From above observation we can say subscriber_by_category: high got maximum 
median views per day count(107318) 

```{r echo=FALSE}
ggplot(aes(y=views/trend_day_count,x=tag_appeared_in_title),data=YtUsa)+
  geom_boxplot()+scale_y_log10(breaks=c(10000,50000,300000))+
  labs(caption="scale_y_log10()")+
  ggtitle("views per day on tag_appeared_in_title(FALSE or TRUE)")
```

```{r echo=FALSE}
with(YtUsa,by(views/trend_day_count,tag_appeared_in_title,summary))
```

Median views per day count for tag_appeared_in_title : True is higher than
the Median views per day count for tag_appeared_in_title : False


```{r echo=FALSE}
ggplot(aes(y=views/trend_day_count,x=comments_disabled),data=YtUsa)+
  geom_boxplot()+scale_y_log10()+labs(caption="scale_y_log10()")+
  ggtitle("views per day on comments_disabled(FALSE or TREU)")
```

```{r echo=FALSE}
ggplot(aes(y=views/trend_day_count,x=ratings_disabled),data=YtUsa)+
  geom_boxplot()+scale_y_log10()+labs(caption="scale_y_log10()")+
  ggtitle("views per day on ratings_disabled(FALSE or TREU)")
```

On a trending video comments_disabled or ratings_disabled has an impact over 
number of viewer per day.

```{r echo=FALSE, message=FALSE}
ggplot(aes(y=views/trend_day_count,x=trend_tag_highest),data=YtUsa)+
  geom_point(alpha=.1)+scale_y_log10()+geom_smooth()+
  labs(caption = "scale_y_log10()")+
  ggtitle("views per day v/s trend_tag_highest")
```

```{r echo=FALSE}
with(YtUsa,cor(views/trend_day_count,trend_tag_highest))
```


Correlation between (views/trend_day_count) & trend_tag_highest is 0.042,
which is slightly better than the correlation between views & 
trend_tag_highest(-0.013),which was calculated during Bivariate Plots Section


```{r fig.width=12, fig.height=8,echo=FALSE}
ggplot(aes(y=views,x=likes,color=trend_day_count),data=YtUsa)+
  geom_point(alpha=.5,size=4,position = "jitter")+coord_cartesian(
    xlim=c(0,quantile(YtUsa$likes,0.95)),
    ylim=c(0,quantile(YtUsa$views,0.95)))+
  ggtitle("top 95% of (views v/s likes) as per trend_day_count")
```

Above plot representing top 95% data of (views v/s likes) coloured by 
different trend_day_count.

```{r fig.width=12, fig.height=8,echo=FALSE}
ggplot(aes(y=views,x=likes),data=YtUsa)+geom_point(
  aes(color=subscriber_by_category),alpha=.25,size=6,shape=6)+
  coord_cartesian(xlim=c(0,quantile(YtUsa$likes,0.95)),
                  ylim=c(0,quantile(YtUsa$views,0.95)))+
  ggtitle("top 95% of (views v/s likes) as per subscription category")
```

Above plot representing top 95% data of (views v/s likes) coloured by 3 
different group of categories by subscription numbers.

Across the plot We can see a clear dominance of group medium & high for high
views count & high likes for Youtube trending videos.

```{r echo=FALSE, fig.height=8,message=FALSE}
ggplot(aes(y=views,x=trend.publish.diff),data=YtUsa)+
  geom_point(position = "jitter",alpha=0.1,color="Orange")+coord_cartesian(
    xlim=c(0,quantile(YtUsa$trend.publish.diff,0.95)))+scale_y_log10()+
  geom_smooth()+facet_wrap(~tag_appeared_in_title)+
  ggtitle("views v/s top 95% trend.publish.diff with respect of 
tag_appeared_in_title or not")+labs(caption = "scale_y_log10()")
```

Above plot showing tag_appeared_in_title has an impact over views v/s top 95%
of trend.publish.diff variables.

```{r fig.width=12, fig.height=8,echo=FALSE}
ggplot(aes(y=views,x=subscriber_by_category,color=trend_day_count),
       data=YtUsa)+geom_jitter(alpha=.5,size=2)+coord_cartesian(ylim=c(
         0,quantile(YtUsa$views,0.95)))+
ggtitle("Top 95% views v/s subscriber_by_category colored by trend_day_count")
```

Above plot representing top 95% views v/s subscriber_by_category data 
coloured by different trend_day_count.

```{r fig.width=12, fig.height=8,echo=FALSE}
ggplot(aes(y=views/trend_day_count,x=subscriber_by_category,
           color=tag_appeared_in_title),data=YtUsa)+geom_jitter()+
  coord_cartesian(ylim=c(0,quantile(YtUsa$views/YtUsa$trend_day_count,.95)))+
ggtitle("Top 95% views per day subscription category wise & differentiate by
tag_appeared_in_title or not")
```

Above plot representing top 95% views per day v/s subscriber_by_category 
color differentiate by tag_appeared_in_title or not.

Now I am plotting same plot,but instated of views per day, this time I am 
using total views of a video.

```{r fig.width=12, fig.height=8,echo=FALSE}
ggplot(aes(y=views,x=subscriber_by_category,color=tag_appeared_in_title),
       data=YtUsa)+geom_jitter()+coord_cartesian(
         ylim=c(0,quantile(YtUsa$views,.95)))+
ggtitle("Top 95% views subscription category wise differentiate by 
tag_appeared_in_title or not")
```

Though last 2 plots looks similar.
But take a close look on y-axis(views) scale value.Its scale value much more
bigger than previous plot, because it represents total views of a video_id,
not average views on a day.


```{r fig.width=15, fig.height=9,echo=FALSE}
with(subset(YtUsa,!is.na(subscriber)),ggplot(aes(
  y=views,x=subscriber,size=trend_day_count),data=subset(
    YtUsa,!is.na(subscriber)))+geom_point(alpha=0.25,position = "jitter")+
  scale_x_continuous(breaks=seq(0,30000000,2000000))+
  scale_y_continuous(breaks=seq(0,150000000,10000000))+
  ggtitle("Views v/s Subscriber size differentiate by trend_day_count"))
```

By taking a closer look on size of the bubble,we can observe,trending videos 
those have listed for more than 5 times got the highest number of views.

There are multiple number of outliers exist in the plot, many trending videos 
got huge number of views ,but their subscriber counts are very less.
Lets focus to 0 to 1000 subscriber and apply facet_wrap for comments_disabled
& ratings_disabled variables.

```{r fig.width=15, fig.height=9 ,echo=FALSE, warning=FALSE}
plt5 <- with(subset(YtUsa,!is.na(subscriber)),ggplot(aes(
  y=views,x=subscriber),data=subset(YtUsa,!is.na(subscriber)))+
  geom_point(alpha=0.25,position = "jitter")+
ggtitle("Views v/s Subscriber differentiate by comments_disabled
(False or True)")+facet_wrap(~comments_disabled)+scale_x_continuous(
  limits = c(0,1000))+scale_y_continuous(limits = c(0,10000000)))

plt6 <- with(subset(YtUsa,!is.na(subscriber)),ggplot(aes(
  y=views,x=subscriber),data=subset(YtUsa,!is.na(subscriber)))+
  geom_point(alpha=0.25,position = "jitter")+
ggtitle("Views v/s Subscriber differentiate by ratings_disabled
(False or True)")+facet_wrap(~ratings_disabled)+scale_x_continuous(
  limits = c(0,1000))+scale_y_continuous(limits = c(0,10000000)))

grid.arrange(plt5,plt6,ncol=1)
```

So we can see, other than ratings_disabled & comments_disabled set to True 
videos ,there are many other outliers present with subscriber = 0 with huge 
number of views.
I don't know, the real reason behind this.It might be there are some lurking
variables, which might be causing this issue.

```{r fig.width=12, fig.height=8, echo=FALSE}
with(subset(YtUsa,!is.na(subscriber)),ggplot(aes(
  y=views,x=subscriber),data=subset(YtUsa,!is.na(subscriber)))+
  geom_point(alpha=0.2,position = "jitter",color="deeppink")+
    coord_cartesian(xlim=c(quantile(subscriber,.025),quantile(
      subscriber,.975)),ylim=c(quantile(views,.025),quantile(views,.975)))+
    facet_wrap(~tag_appeared_in_title)+
ggtitle("2-Tailed 95% CI (Views v/s Subscriber) differentiate by 
tag_appeared_in_title(False or True)")+geom_smooth(method="lm",color="red")) 
```

```{r echo=FALSE}
with(subset(YtUsa,!is.na(subscriber) & tag_appeared_in_title),cor(
  views,subscriber))
```

PCC between views & subscriber with respect of tag_appeared_in_title : True 
= 0.27

```{r echo=FALSE}
with(subset(YtUsa,!is.na(subscriber) & !tag_appeared_in_title),cor(
  views,subscriber))
```

PCC between views & subscriber with respect of tag_appeared_in_title : False
= 0.24 .

From the last plot & above observations ,it could be said ,that correlation 
between views & subscriber when tag appeared in the title is more stronger 
than when tag does not appear in the title.

On other words, if a trending video title does not contain any tag of it,then
its number of subscriber & views counts might also get affected(lower).


```{r fig.width=15, fig.height=9 ,echo=FALSE}
with(subset(YtUsa,!is.na(subscriber)),ggplot(aes(
y=views/trend_day_count,x=subscriber,color=category_id,size=trend_day_count),
data=subset(YtUsa,!is.na(subscriber)))+
  geom_point(alpha=0.25,position = "jitter")+
  coord_cartesian(xlim = c(quantile(subscriber,.025),quantile(
    subscriber,.975)),ylim =c(quantile(views/trend_day_count,.025),quantile(
      views/trend_day_count,.975)))+
ggtitle("2-Tailed 95% CI (Views per day v/s Subscriber) categorized & colored
by category_id and differentiate by tag_appeared_in_title(False or True) and
sized by trend_day_count")+
  ylab("views per day")+facet_wrap(category_id~tag_appeared_in_title)) 
```

From the above plot(I considered 2-tailed 95% CI) we can see ,there are few 
categories where variance of views per day & subscribe are very big.
Categories are : 10,23,24.

Also we can say,the video channel, which had the highest level of subscribers
for Youtube trending videos, is belongs to category_id: 23

```{r fig.width=15, fig.height=9, echo=FALSE}
with(subset(YtUsa,!is.na(subscriber)),ggplot(aes(
 y=views,x=subscriber,size=trend_day_count)
 ,data=subset(YtUsa,!is.na(subscriber)))+
   geom_point(alpha=0.25,position = "jitter",color="navyblue")+
  coord_cartesian(xlim = c(quantile(subscriber,.025),quantile(
    subscriber,.975)),ylim =c(quantile(views,.025),quantile(
    views,.975)))+
ggtitle("2-Tailed 95% CI (Views v/s Subscriber) categorized by 
subscriber_by_category and differentiate by tag_appeared_in_title
(False or True) and sized by trend_day_count")+
  facet_wrap(subscriber_by_category~tag_appeared_in_title,ncol=2))
```

From the above plot(I considered 2-tailed 95% CI) we can say,video belongs to 
categories where they have highest level of subscribers;those videos are 
using at least one of its tag on the trending video title.


Lest's print out the model table :-

```{r echo=FALSE}
mtable(m1, m2, m3, m4, m5,m6,m7, sdigits = 3)
```


Now summary of final model :-

```{r echo=FALSE}
summary(m7)
```

R^2 value of the final model collectively explains only about 79 percent of 
the variance in views.
Residual standard error: 2112000 on 4301 degrees of freedom.


# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the 
# investigation. Were there features that strengthened each other in terms 
# of looking at your feature(s) of interest?

I observed,by just seeing how many times a video get appeared on the Youtube 
trend,we can't imagine how many views a video can get,because variance of 
views for each day is very big.

Median views per day for subscriber_by_category: low = 36099 .
Median views per day for subscriber_by_category: medium = 62628 .
Median views per day for subscriber_by_category: high = 107318 .

Median views per day count for tag_appeared_in_title : True is 82070 .
Median views per day count for tag_appeared_in_title : False is 55604 .

Video channel which had the highest level of subscribers for Youtube trending
videos,belongs to category_id = 23 .

From top 95% data points of views per day & subscriber,we observed there are
few categories where variance of views & subscribe are very big. 
Categories are : 10,23,24 .

From plots,I saw many of videos have only 0 like, but have higher number of 
views.
And many of videos have zero(0) subscriber,but still get to manage higher 
number of viewers; those are probably the outlier of the dataset.
To filter them,I focused on 0 to 1000 subscriber and apply facet_wrap for 
comments_disabled & ratings_disabled variables.
But surprisingly,comments_disabled=TRUE & ratings_disabled=TRUE ,could not be
able to filter out all of the outliers.
There must be something else going on ,may be some lurking variables causing
this nature.

Trending videos those have listed for more than 5 times(or days), got 
the highest number of views count.
Pearson Coefficient Correlation(PCC) between views & subscriber is more 
stronger when one of its tag appeared in the title.
Variance of views per day is getting bigger for higher number of subscriber
groups(low < medium < high for subscriber_by_category).

### Were there any interesting or surprising interactions between features?

Yes,
Many of the trending videos have lower number of subscriber & yet they 
managed to get more number of viewers than top subscriber channels.
Also I saw there are many trending videos managed to get higher number of 
views counts,but they have very few likes, many of them have 0 like only,
I think some of 0 like videos came from videos where ratings_disabled set 
to True.

### OPTIONAL: Did you create any models with your dataset? 
# Discuss the strengths and limitations of your model.

Yes,
For the final model(m9) ,I got Multiple R-squared:  0.7902 & Residual 
standard error: 2112000 .
So R^2 value of the final model collectively explains only about 79 percent 
of the variance in views.
Also its Residual standard error is very big here & that would cause a large 
range of Confidence Interval for predictive model. 
In other words standard error is bigger for the final model.
Therefore this model would not be able to calculate/predict views counts 
accurately.

The model I am looking for, not just for predicting views count of a trending
video;I want to flag a video, if its fall behind 95% CI.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}
ggplot(aes(x=trend_day_count),data=YtUsa)+geom_histogram(
  binwidth =1,color="black",fill="white")+
  scale_x_continuous(breaks=seq(1,15,1))+
  scale_y_continuous(breaks=seq(0,700,100))+
  xlab("No. of days or times a video trended")+ylab("Frequency")+
labs(caption="105 days of Youtube Trending videos for 4547 unique video id's")+
  ggtitle("Distribution of 'trend_day_count' variable")
```

### Description One

From the above plot, we can analyze that no video trended over 14-day period.
We can see there are more than 600 videos those were appeared in the Youtube
trending video list for only once(that was the first & last time). 


### Plot Two
```{r echo=FALSE,message=FALSE, fig.width=8, fig.height=5, Plot_Two}
ggplot(aes(y=views,x=likes+1),data=YtUsa)+
  geom_jitter(alpha=0.1,size=2,color="orange")+
  scale_x_log10(breaks=c(1,100,1000,10000,100000,1000000))+scale_y_log10(
    breaks=c(1,1000,5000,10000,50000,100000,500000,1000000,5000000,10000000,
             50000000,100000000))+
  xlab("No. of likes received + 1")+ylab("No. of viewers watched")+
  labs(caption="Youtube Trending videos for 4547 unique video id's")+
ggtitle("Views v/s (Likes+1) with log10 transformation for both axes 
+ smoother lines")+
  geom_smooth()+geom_smooth(method="lm",color="red")
```


### Description Two

Since log10 applied on the x-axis & and there are few videos in Youtube 
trending list with 0 likes, because of this, we have to pass the 
variable (likes+1) instead of likes into the scale_x_log10() function.
That would help to overcome infinite values(since log10(0) = Inf).
Therefore on the above plot, on x-axis, x=1 represents 0 like and x=100 
represents 99 likes and so on.

I have applied two smoother lines on the above plot ,one with linear method
(red line) & another without linear method(blue line).
Here smoother line(Slope Of Regression Line) represents the slope of the line
of best fit in the scatterplot.
Since there is very strong relationship between views & likes attribute 
(cor=0.82),hence the slope of the linear line nearer to 1. 

We can see there are many outliers exist on y-axis for x = 1 .
Many of those video authors might disable video rating ,so users are not able
to like or dislike the video.
Those outliers causing non-linear regression line to start from (x=1,y=10000).


### Plot Three
```{r echo=FALSE,fig.width=15, fig.height=9, message=FALSE,Plot_Three}
with(subset(YtUsa,!is.na(subscriber)),ggplot(aes(y=views,x=subscriber),
  data=subset(YtUsa,!is.na(subscriber)))+geom_point(aes(
    size=trend_day_count),alpha=0.25,position = "jitter",color="navyblue")+
  coord_cartesian(xlim = c(quantile(subscriber,.025),quantile(
    subscriber,.975)),ylim =c(quantile(views,.025),quantile(views,.975)))+
  scale_x_continuous(breaks=c(0,2000000,7000000,10000000,15000000,17000000))+
  scale_y_continuous(breaks=c(0,2000000,6000000,8000000))+
ggtitle("2-Tailed 95% CI (Views v/s Subscriber) categorized by 
subscriber_by_category and differentiate by tag_appeared_in_title
(False or True) and sized by trend_day_count")+
xlab("No. of subscriber of the video channel")+ylab("No. of viewers watched")+
  labs(caption="Youtube Trending videos for 4547 unique video id's")+
  facet_wrap(subscriber_by_category~tag_appeared_in_title,ncol=2)+
  geom_smooth(method="lm",color="red")+geom_smooth())
```

### Description Three

Notice - I took the subset of the dataset to filter out subscriber with NA.

After considering only top 95% viewers & subscribers, we can see ,under any 
group, trending videos those have not included any of its tag on the video 
title,tend to have lower number of subscriber & viewers, than videos those 
have included one(at least).

Trending Videos under subscriber_by_category: high & subscriber_by_category:
medium were able to achieve highest level of views in Youtube.

From bubble size ,we can say ,trending Videos those have trended for more 
than 3 to 4 times(or days),were able to achieve highest level of viewers 
in Youtybe.

From linear regression line ,we can say,other than videos under 
subscriber_by_category: low,as per average number of subscriber increases,
average number of viewers also increases.


------

# Reflection


The Youtube Trending data set contains information on almost 4,600 unique 
videos across 23 variables.And it is recorded for total 105 days.
[I have a created a categorical variable extra though.]

I started by understanding the individual variables in the data set, and then
I explored interesting questions and leads as I continued to make 
observations on plots.
Eventually, I explored the views of videos across many variables.
Views count of a video strongly correlated with likes,dislikes,comment_count.
Highest correlation exist between views & likes variables,where cor=0.82 .
But there exist some other important features :subscriber,trend_day_count,
category_id; they have good correlation values.
That's why I include all of the above features to build predictive model.
Model was able to account for only 79% of the variance in the dataset.
Also model Residual standard error was big.So model would not be very useful
to predict views count accurately for a Youtube trending video.

Right now,I might be unable to build a good predictive model,but I found some
interesting facts about Youtube trending videos; these are:-
84% or more trending videos are using one of its tag on the video title for 
at least once.
Other than 604 trending videos,all trending videos are appeared in the 
trending list for more than 1 once.
Maximum number of Youtube videos are listed on trending, within 0 to 14 days
of the video publishing date.
More users engaged in conversation when they were disliking a trending video
rather than liking a trending video.
If difference between first trending date & publish date is less than 4 days,
then there is a big chance,that video would not be re-trended for more than 
3 times.
There is a impact on Youtube trending videos views count over 
tag_appeared_in_title or not.
Trending videos those have listed for more than 5 times got the highest 
number of views.
Videos belongs to categories where number of subscriber is/are most ;those 
videos are using at least one of its tag on the trending video title.


Struggle:-

I struggled to create these two variables : trend_tag_highest, 
trend_tag_total .

I failed to create these two variables from the dataset directly;it might 
happen,since I was new in R-Programming.

But some how,by creating a separate(temporary) dataframe from 'tags' variable
and by using that temporary dataframe,I succeed to create those new 
variables: trend_tag_highest, trend_tag_total .
Trick behind this was to create a similar data structure of Python dictionary
in R-Programming.
Though I believe there should be some easy technique to achieve the same goal.


Surprise:-

Many of Youube trending videos get listed on trending list for more than 1 
time(or day), but they did not get higher number of traffics.

Another point I already discussed,many of the trending videos have lower
number of subscriber(some of them have 0) & yet they managed to get greater
number of viewers than top subscriber channels present in the Youtube.
Also I saw there are many trending videos managed to get higher number of 
views counts,but they have very few likes(many of them have 0).


Future work :-

In future we could use a OCR(Optical character recognition) technique to scan 
the thumbnail image to observe whether the thumbnail using any text or not.

We can make a new variable called 'tag_appeared_in_description' with the help
of 'tags' & 'description' variables,it would be very similar to the variable 
already exist: 'tag_appeared_in_title' .
With similar approach, we can make another variable called 
'title_appeared_in_desccription' with the help of 'title' & 'description' 
variables.

We can create some bucket variables(using cut function) for 
'last_tredning_date' and 'tags_count' variable to make really use of those 
2 features. 

We can do some element grouping,that might help to extract some hidden 
information from the data.


Limitation of the dataset:-

There exist a latency(time delay) in the dataset,happened due to scrapping 
the subscriber column data separately(Subscriber data did not come with the 
original dataset,so it is recorded during different time).


Possible Lurking Variables :-

There are some lurking variables those could affect the main features of the
dataset(views,likes,dislikes,comment_count,subscriber).For example what is 
the content of the video thumbnail,which is used in the trending video.A auto
generated thumbnail(by Youtube system) might cause lower number of views,
likes,etc.While on the other hand, if a trending video using a custom 
thumbnail or a thumbnail which was manually uploaded by the author.And if its
containing a perfect image or a text that could provoke viewers to click and 
check the video(in other word Clickbait),that would affect the trending 
statistic easily. 

Alternatively, if a trending video containing a content which was the trend 
of the day on the Internet,then it could easily get more attention than 
any other trending videos irrespective of how many subscriber the video 
channel had.

Another thing,video might not well presented,either its graphics or sound 
quality was poor or presentation was poor.

It is also possible that some dishonest users are using some blackhat 
technique to bypass Youtube trending algorithm.And still yet Youtube 
algorithms did not flag it.


